`flippant` -- An `R` package for the automated  analysis of dithionite

### 2015-09-16 inst/manuscript/manuscript.rmd
Do not use a TOC;

---
title: "`flippant` -- An `R` package for the automated  analysis of dithionite 
  scramblase assays"
author: "Johannes Graumann ^†,^*, Birgit Ploier ^‡^, Richard J. Cotton ^†^,
  Mike A. Goren ^‡^ and Anant K. Menon ^‡^"
date: "September 16, 2015"
output: 
#  word_document
  pdf_document:
    toc: false
    toc_depth: 2
    fig_caption: yes
#bibliography: flippant.bib
#csl: cell.csl
---

>>>>

---
title: "`flippant` -- An `R` package for the automated  analysis of dithionite 
  scramblase assays"
author: "Johannes Graumann ^†,^*, Birgit Ploier ^‡^, Richard J. Cotton ^†^,
  Mike A. Goren ^‡^ and Anant K. Menon ^‡^"
date: "September 16, 2015"
output: 
#  word_document
  pdf_document:
    fig_caption: yes
#bibliography: flippant.bib
#csl: cell.csl
---
